The Emergent Simplicity of Galaxy Size

### 2017-09-15 paper/galsize_paper.tex
Added description of Moster13-based smhm

>>>>

We map $\mstar$ onto subhalos with the best-fit stellar-to-halo mass relation from \citet{moster_etal13}:

\begin{equation*}
\mstar/\mhalo = 2N\left[(\mhalo/M_{1})^{-\beta} + (\mhalo/M_1)^{\gamma}\right]^{-1}.
\end{equation*}
For halo mass $\mhalo$ we use $\mpeak,$ the largest value of $\mvir$ ever attained along the main progenitor branch of the subhalo. The values of the best-fit parameters in \citet{moster_etal13} were fit to a stellar mass function (SMF) with values $\mstar^{\rm MPA-JHU}$ based on the MPA-JHU catalog \citep{kauffmann_etal03,brinchmann_etal04}, which differs from the SMF in our galaxy sample \citep[see, e.g.,][]{bernardi_etal14}. We account for this difference by manually tabulating the median value $\langle\mstar^{\rm Meert+15}\vert\mstar^{\rm MPA-JHU}\rangle$ in logarithmic bins spanning $9 < \log_{10}\mstar^{\rm MPA-JHU}/\msun < 12,$ and applying the median correction to the Monte Carlo realization of the mock galaxy sample. This results in a typical boost of $\sim0.25$ dex at $\mstar^{\rm MPA-JHU}\approx10^{9.75}\msun,$ and $\sim0.4$ dex at $\mstar^{\rm MPA-JHU}\approx10^{11.5}\msun.$
